Looking for CDI Bias: WG Comprehension

### 2021-08-02 02-preliminary-WGcomp.Rmd
finished running some comprehension DIF stats

save(file = here("data/eng_wg_comp_sex_sexDIF.Rds"), 
     mg1, mg2, mg3, mg4, m_sc2, mod_sc1, mod_fullconstrain) 
```

@@

# same item estimates with/without free_means? 
cor(mg2_df$d_f, mg3_df$d_f) # .999
cor(mg2_df$d_m, mg3_df$d_m) # .999

anova(mg1, mg2) # AIC and BIC prefer slope-invariant model (mg2)
anova(mg2, mg3) # AIC/BIC prefer mg3, with varying group means
```

@@

#DIF(mg2, c('d')) # No hyper-parameters were estimated in the DIF model. For effective DIF testing, freeing the focal group hyper-parameters is recommended.

@@

save(file = here("data/eng_wg_comp_SES_DIF.Rds"), 
     mg1, mg2, mg3, m_sc2, mod_sc1, mod_fullconstrain)
```

@@

>>>>

mirtCluster()
mg3_dif = DIF(mg3, c('d'))

save(file = here("data/eng_wg_comp_sex_sexDIF.Rds"), 
     mg3_dif, mg1, mg2, mg3, mg4, m_sc2, mod_sc1, mod_fullconstrain) 
```

@@

# same item estimates with/without free_means? 
#cor(mg2_df$d_f, mg3_df$d_f) # .999
#cor(mg2_df$d_m, mg3_df$d_m) # .999

#anova(mg1, mg2) # AIC and BIC prefer slope-invariant model (mg2)
#anova(mg2, mg3) # AIC/BIC prefer mg3, with varying group means
```

### Items with DIF in difficulty

`r nrow(subset(mg3_dif, p<.05))` items show DIF based on a $\chi^2$ test yielding $p<.05$.
Below we show the `r nrow(subset(mg3_dif, p<.001))` items with $p<.001$.

```{r}
mg3_dif %>% arrange(BIC) %>% filter(p < .001) %>%
  select(-AICc, -SABIC, -HQ, -df) %>%
  kable(digits = 2, format = "html", table.attr = "style='width:40%;'")
```

@@

#DIF(mg1, c('d')) # No hyper-parameters were estimated in the DIF model. For effective DIF testing, freeing the focal group hyper-parameters is recommended.

@@

mg2_dif = DIF(mg2, c('d')) # No hyper-parameters were estimated in the DIF model. For effective DIF testing, freeing the focal group hyper-parameters is recommended.
mg3_dif = DIF(mg3, c('d')) # (though varying group mean not justified according to AIC/BIC)

save(file = here("data/eng_wg_comp_SES_DIF.Rds"), 
     mg1, mg2, mg3, m_sc2, mod_sc1, mod_fullconstrain,
     mg2_dif, mg3_dif)
```

@@

### Items with DIF in difficulty

`r nrow(subset(mg3_dif, p<.05))` items show DIF based on a $\chi^2$ test yielding $p<.05$.
We show these items below.

```{r}
mg3_dif %>% arrange(BIC) %>% filter(p < .05) %>%
  select(-AICc, -SABIC, -HQ, -df) %>%
  kable(digits = 2, format = "html", table.attr = "style='width:40%;'")
```
